Papers I Love

### 2017-06-26 texts/dev/PapersILove.tex
.

\subsubsection{Patterns}
\begin{enumerate}
	\item {Active Object: An Object Behavioral Pattern for Concurrent Programming\\
\url{http://www.cs.wustl.edu/~schmidt/PDF/Act-Obj.pdf}}
	\item {Plop Half-Sync/half-Async: An Architectural Pattern for Efficient and Well-Structured Concurrent I/o\\
\url{http://www.cs.wustl.edu/~schmidt/PDF/PLoP-95.pdf}}
\end{enumerate}

@@

\subsection{Text Mining}
\begin{enumerate}
	\item {Text Mining Infrastructure in R\\ \url{https://www.jstatsoft.org/article/view/v025i05}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}

>>>>

\subsubsection{Patterns}
\begin{enumerate}
	\item {Active Object: An Object Behavioral Pattern for Concurrent Programming\\
\url{http://www.cs.wustl.edu/~schmidt/PDF/Act-Obj.pdf}}
	\item {Plop Half-Sync/half-Async: An Architectural Pattern for Efficient and Well-Structured Concurrent I/o\\
\url{http://www.cs.wustl.edu/~schmidt/PDF/PLoP-95.pdf}}
	\item{EASTL -- Electronic Arts Standard Template Library \url{http://www.open-std.org/jtc1/sc22/wg21/docs/papers/2007/n2271.html}}
\end{enumerate}

@@

\subsection{Text Mining}
\begin{enumerate}
	\item {Text Mining Infrastructure in R\\ \url{https://www.jstatsoft.org/article/view/v025i05}}
	\item {Checkers Is Solved\\ \url{http://www.eecs.wsu.edu/~holder/courses/CptS570/fall07/papers/Schaeffer07.pdf}}
	\item{Mastering the Game of Go with Deep Neural Networks and Tree Search  \url{https://gogameguru.com/i/2016/03/deepmind-mastering-go.pdf}}
\end{enumerate}

@@

\section{Mathematics}
\subsection{Real Analysis}
\begin{enumerate}
	\item {Coisas que o Luís precisa aprender\\
\url{http://www.todasasconfiguracoes.com/wp-content/uploads/2012/04/luis.pdf}}
\end{enumerate}
\subsection {Statistics}
\begin{enumerate}
	\item {A Note on the Generation of Random Normal Deviates\\
\url{http://projecteuclid.org/euclid.aoms/1177706645}}
	\item {Tidy Data\\
\url{http://vita.had.co.nz/papers/tidy-data.pdf}}
	\item {A Tutorial on Principal Component Analysis - Derivation, Discussion and Singular Value Decomposition\\
\url{https://www.cs.princeton.edu/picasso/mats/PCA-Tutorial-Intuition_jp.pdf}}
	\item{An introduction to ROC analysis\\
\url{https://ccrma.stanford.edu/workshops/mir2009/references/ROCintro.pdf}}
	\item{TEACHING SURVEY SAMPLING WITH THE ‘SAMPLING’ R PACKAGE  \url{http://iase-web.org/documents/papers/icots8/ICOTS8_4J1_TILLE.pdf}}
\end{enumerate}
\subsection{Forecast}
\begin{enumerate}
	\item {Forecasting Global Climate Change\\
\url{https://faculty.wharton.upenn.edu/wp-content/uploads/2015/02/GlobalClimateChange-FWP-(2)_2.pdf}}
\end{enumerate}
